Fourmile_inputs

### 2022-09-30 fourmile_inputs.Rmd
finished input files

bet_rain <- bet_met %>%
  dplyr::select(c(5,6)) %>%
  rename(Betasso_rain =1) %>%
  mutate(date = as.Date(DATE_TIME)) %>%
  group_by(date) %>%
  summarize(Betasso = sum(Betasso_rain)) %>%
  filter(date > '2009-12-31')

@@

updated_prec <- updated_prec %>%
  mutate_at(c(2,4,6,8,10), ~(.*25.4)) %>%
  rename(GH = 2,
         LM = 4,
         SE = 6,
         SP = 8,
         ST = 10)

gh <- updated_prec %>%
  dplyr::select(c(1,2)) %>%
  mutate(date = mdy(GH_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

lm <- updated_prec %>%
  dplyr::select(c(3,4)) %>%
  mutate(date = mdy(LM_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

se <- updated_prec %>%
  dplyr::select(c(5,6)) %>%
  mutate(date = mdy(SE_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

sp <- updated_prec %>%
  dplyr::select(c(7,8)) %>%
  mutate(date = mdy(SP_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

st <- updated_prec %>%
  dplyr::select(c(9,10)) %>%
  mutate(date = mdy(ST_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

write.csv(gh, 'gh.csv')
write.csv(lm, 'lm.csv')
write.csv(se, 'se.csv')
write.csv(sp, 'sp.csv')
write.csv(st, 'st.csv')

write.csv(precall, 'precall_fix.csv')

# mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
#   replace(is.na(.), -9999) %>%
#   dplyr::select(-c(doy))

>>>>

bet_rain <- bet_met %>%
  dplyr::select(c(5,6)) %>%
  rename(Betasso_rain = 1) %>%
  mutate(date = as.Date(DATE_TIME)) %>%
  group_by(date) %>%
  summarize(Betasso = sum(Betasso_rain)) %>%
  filter(date > '2009-12-31')

@@

updated_prec1 <- updated_prec %>%
  mutate_at(c(2,4,6,8,10), ~(ifelse(. > 7, NA, .))) %>%
  mutate_at(c(2,4,6,8,10), ~(.*25.4)) %>%
  rename(GH = 2,
         LM = 4,
         SE = 6,
         SP = 8,
         ST = 10)

gh <- updated_prec1 %>%
  dplyr::select(c(1,2)) %>%
  mutate(date = mdy(GH_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE) %>%
  arrange(date)

gh_old <- precall %>%
  dplyr::select(c(date, GH)) %>%
  filter(date < '2016-01-01') %>%
  bind_rows(gh_old, gh) %>%
  distinct(date, .keep_all = TRUE)

precall <- precall %>%
  dplyr::select(-c(GH))

precall <- full_join(precall, gh_old, by='date')

lm <- updated_prec1 %>%
  dplyr::select(c(3,4)) %>%
  mutate(date = mdy(LM_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE) %>%
  arrange(date)

lm_old <- precall %>%
  dplyr::select(c(date, LM)) %>%
  filter(date < '2016-01-01')

lm_old <- bind_rows(lm_old, lm) %>%
  distinct(date, .keep_all = TRUE)

precall <- precall %>%
  dplyr::select(-c(LM))

precall <- full_join(precall, lm_old, by='date')

se <- updated_prec1 %>%
  dplyr::select(c(5,6)) %>%
  mutate(date = mdy(SE_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE) %>%
  arrange(date)

se_old <- precall %>%
  dplyr::select(c(date, SE)) %>%
  filter(date < '2016-01-01')

se_old <- bind_rows(se_old, se) %>%
  distinct(date, .keep_all = TRUE)

precall <- precall %>%
  dplyr::select(-c(SE))

precall <- full_join(precall, se_old, by='date')

sp <- updated_prec1 %>%
  dplyr::select(c(7,8)) %>%
  mutate(date = mdy(SP_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE) %>%
  arrange(date)

sp_old <- precall %>%
  dplyr::select(c(date, SP)) %>%
  filter(date < '2016-01-01')

sp_old <- bind_rows(sp_old, sp) %>%
  distinct(date, .keep_all = TRUE)

precall <- precall %>%
  dplyr::select(-c(SP))

precall <- full_join(precall, sp_old, by='date')

st <- updated_prec1 %>%
  dplyr::select(c(9,10)) %>%
  mutate(date = mdy(ST_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE) %>%
  arrange(date)

st_old <- precall %>%
  dplyr::select(c(date, ST)) %>%
  filter(date < '2016-01-01')

st_old <- bind_rows(st_old, st) %>%
  distinct(date, .keep_all = TRUE)

precall <- precall %>%
  dplyr::select(-c(ST))

precall <- full_join(precall, st_old, by='date')

prec_final <- precall %>%
  mutate_at(c('GH', 'LM', 'SE', 'SP', 'ST'),
            ~(ifelse(!doy %in% c(152:258),
                               NA, .))) %>%
  filter(date < '2021-01-01') %>%
  mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
  dplyr::select(-c(doy))

write.csv(prec_final, 'prec_use.csv')

#check the date range, make sure tip bucekts are being used at right times
# mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
#   replace(is.na(.), -9999) %>%
#   dplyr::select(-c(doy))
